### 2016-05-09 paper/paper.tex
add some references

Although the malicious proof-of-work only works against websites that support
TLS 1.2, as of April 2016, over 56\% of the Alexa top million websites support
this version of TLS~\cite{censys}. Furthermore, we expect this number to
increase as TLS support becomes more widespread~\cite{letsencrypt}.

>>>>

Although the malicious proof-of-work only works against websites that support
TLS 1.2, as of April 2016, over 56\% of the Alexa top million websites support
this version of TLS according to censys.io~\cite{censys}. Furthermore, we
expect this number to increase as TLS support becomes more
widespread~\cite{letsencrypt}.
